### 2023-11-03 sections/experience.tex
Update experience.tex

@@

\begin{cventries}
\cventry
{Lecturer} 
{Universidad de Santiago de Chile} 
{Santiago, CHL} 
{2014 - 2019}
{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}

@@

\cventry
{Lecturer} 
{Universidad de Chile} 
{Santiago, CHL} 
{2013 - 2016}
{School of Government and Public Management, Institute of Public Affairs}\vspace{1.5mm}
\end{cventries}
\pagebreak

>>>>

\cvsection{Current Positions}

\begin{cventries}
\cventry
{Post-Doctoral Researcher in Computational Social Sciences} 
{Leiden University} 
{The Hague, NLD} 
{starting Dec. 1, 2023 - 2026}
{Institute of Public Administration, Faculty of Governance and Global Affairs} \vspace{1.5mm}

\cventry
{Instructor Professor} 
{Universidad de Santiago de Chile (USACH)} 
{Santiago, CHL} 
{2019 - on leave}
{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}
\end{cventries}

@@

\begin{cventries}
\cventry
{Adjunt Professor} 
{Universidad de Santiago de Chile (USACH)} 
{Santiago, CHL} 
{2014 - 2019}
{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}

@@

\cventry
{Lecturer} 
{Universidad de Chile} 
{Santiago, CHL} 
{2013 - 2016}
{School of Government and Public Management, Institute of Public Affairs}\vspace{1.5mm}
\end{cventries}
%% \pagebreak
